### 2022-02-19 misc/solutions/prob-method-sols.tex
1.5

>>>>

\proclaim \llap{*}Exercise 1.5. Let $G=(V,E)$ be a graph on $n\ge 10$ vertices and suppose that if we add
to $G$ any edge not in $G$, the number of copies of a complete graph on $10$ vertices in it increases.
Show that the number of edges of $G$ is at least $8n-36$.

\proof The figure $8n-36$ in the conclusion obscures the fact that we should use Theorem 1.3.3. In
fact,
$$8n-36 = {n^2-n-n^2+17n-72\over 2} = {n(n-1) - (n-8)(n-9)\over 2} = {n\choose 2}-{n-8\choose 2}.$$
Let $F = V^{(2)}\setminus E = \{A_1, A_2,\ldots, A_h\}$ be the set of non-edges in $G$. Since the addition
of any non-edge causes the number of $K_{10}$ subgraphs to increase, we know that for each $A_i$ there
exists a set $X_i$ of size $8$ and disjoint from $A_i$ such that the subgraph induced on
the vertices $A_i\cup X_i$ would be a $K_{10}$ if $A_i$ happened to be in $E$ (which it isn't).
Set $B_i = V\setminus (A_i\cup S_i)$. Clearly, $A_i\cap B_i = \emptyset$ for all $i$. Also,
since $A_i\cup S_i$ is complete except for one missing edge $A_i$, for any $j\ne i$, we have
$A_j\not\subseteq A_i\cup S_i$. This means that $A_j\cap B_i\neq\emptyset$ for all $j\ne i$. Hence
$\bigl\{(A_i,B_i)\bigr\}_{i=1}^h$ is a $(2,n-10)$-system as defined in the chapter, and by
Theorem~1.3.3, $|F| = h\le {2+n-10\choose 2}$. We conclude that $|E|\ge {n\choose 2}-{n-8\choose 2}$.\slug
